Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
minor \"fixes\"

\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{multirow}
\title{Spec2Fab: A  Graph-Based Framework for Fabricating Fabrication Algorithms}

@@

 \teaser{
   \begin{subfigure}[b]{0.2\textwidth}
	\centering
    	\includegraphics[width=\textwidth]{figure/globe.png}
      	\caption{}
        \label{teaser:original}
        \end{subfigure}
        ~ 
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/map.png}
                \caption{}
                \label{teaser:ours}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/chess.png}
                \caption{}
                \label{teaser:makerbot}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/caustics.png}
                \caption{}
                \label{teaser:objet}
        \end{subfigure}
        \caption{Various effects printed with a 3D printer.
        	(a)(b)textured models,(c)a model with a subsurface-scattering resembling a marble chess-board.
        	(d)a caustics image projected by an object under proper lighting}\label{teaser}
 }

@@

\begin{abstract}
Computational fabrication problems are often concerned with optimal material assignment. They attempt to compute a spatially varying material distribution that yields specified real-world behavior. In this paper we introduce Spec2Fab, a graph based framework that simplifies the design, development and implementation of these algorithms. We illustrate the utility of our framework by giving showing implemented fabrication algorithms as well as their manufactured results. 
\end{abstract}

@@

\note{Teaser should be all different results produced using spec2Fab, texture, subsurface scattering, caustics etc...}

@@

Computing material assignments at output device resolution is computationally inefficient. Because of this, material assignments are computed  using a reduced representation. We specify this representation using a Reducer Network.  This structure is conceptually similar to those used in programmable shading systems (e.g. ~\cite{Cook1984}, Maya Shader Networks) . However these systems are primarily concerned with assigning known materials and textures to an object's surface whereas we are seeking a volumetric assignment of (as yet) unknown materials. In order to accomplish this task we build a directed, acyclic graph which has the object's surface geometry as its root node. We define two classes of nodes, geometry nodes and parameterization nodes. A geometry node takes a volumetric region as input and produces a partition of unity of this region as output. The leaf nodes of our graph are the parameterization nodes which associate a material assignment function of the form $\lambda\left(x,y,z,\theta\right)$ to an input volumetric region. Lambda can either output material parameters or a discrete material assignment for a spatial point $\left(x,y,z\right)$ given some parameters, here denoted by $\theta$. We allow our material assignment nodes to assign a void material to regions of the mesh. This allows us to treat surface displacements and material assignments in a unified fashion. Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node. We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph, however, for material assignment problems this is neither required nor desired.

@@

\subsection{Tuners}
We define tuners as an abstract interface between a Reducer Node and an optimization algorithm.  Specifically a tuner is comprised of an optimization scheme, an error metric and a goal. Each tuner is attached to a specific geometric node in the Reducer Network. It then acts to optimize, or tune, the free variables associated with the subtree rooted at this node. One can think of this as a self-tuning shader network.  This organizational structure allows us to easily optimize subdomains of our object using different tuners. We provide a mechanism for scheduling tuner execution thus allowing both serial and parallel processing. 
\subsection{Tuning the Reducer Network}
\autoref{fig:tuner0} shows a typical workflow for a tuner.
\begin{figure}
\includegraphics[width=0.4\textwidth]{figure/tuner0.png}
\caption{Typical workflow for a Tuner.}
\label{fig:tuner0}
\end{figure}
A Tuner initializes its optimization procedure by querying the search space from its Reducer Node.
The Reducer Node computes the search space by traversing its sub-tree and collecting
free variables. The search space specifies the number of free variables, the type of each free variable
(discrete or continuous) and the bounds of these variables. 
With the search space specified, the Tuner's optimization subroutine executes.
The optimization subroutine may ask for additional information such as
the error value of a variable assignment and the gradient. These queries are answered
with call-back functions set up by the Tuner before executing the optimization subroutine. 
The call-back function typically performs the following three steps:
using Reducer Node to convert a variable assignment back to material assignment
over the volume, running simulation with the new material assignment
and computing errors given the simulated result.
We note that gradient computation of our material function $\lambda$ can be performed by efficiently traversing the Reducer Network.
\subsection{Tuner Network}
For many fabrication problems, tuners cannot act in isolation. For instance,  occasionally the best material at a given point in space is dependent upon the material assignment at nearby locations.  Tuning the free variables as if they were independent usually yields unsatisfactory results. Therefore, we allow the tuner to share information according to a user-specified graph structure.  This allows our framework to be interfaced with a wide range of existing graph based optimization and inference algorithms. For example, consider the Floyd–Steinberg dithering algorithm where the error of a pixel is distributed
to $4$ of its neighbors (right, lower left, down and lower right).  The graph structure of this algorithm is illustrated in Figure~\ref{fig:tuner}. The tuner is combined with the Reducer Network in Figure~\ref{fig:red1}. A simplified view of the combined graph is shown in Figure~\ref{fig:combine}. Executing each tuner in order is equivalent to running the Floyd–Steinberg dithering algorithm.

>>>>

\usepackage{amsfonts}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{multirow}
\title{Spec2Fab: A  Graph-Based Framework for Fabricating Fabrication Algorithms}

@@

 \teaser{
   \begin{subfigure}[b]{0.2\textwidth}
	\centering
    	\includegraphics[width=\textwidth]{figure/globe.png}
      	\caption{}
        \label{teaser:original}
        \end{subfigure}
        ~ 
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/map.png}
                \caption{}
                \label{teaser:ours}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/chess.png}
                \caption{}
                \label{teaser:makerbot}
        \end{subfigure}
        ~
        \begin{subfigure}[b]{0.2\textwidth}
                \centering
    	\includegraphics[width=\textwidth]{figure/caustics.png}
                \caption{}
                \label{teaser:objet}
        \end{subfigure}
        \caption{3D-printed objects with various effects designed by our API.
        	(a)(b)textured models,(c)a model with a subsurface-scattering resembling a marble chess-board.
        	(d)a caustics image projected by an object under proper lighting}\label{teaser}
 }

@@

\begin{abstract}
Computational fabrication problems are often concerned with optimal material assignment. They attempt to compute a spatially varying material distribution that yields specified real-world behavior. In this paper we introduce Spec2Fab, a graph based framework that simplifies the design, development and implementation of these algorithms. We illustrate the utility of our framework by 
showing implemented fabrication algorithms as well as their manufactured results. 
\end{abstract}

@@

%\note{Teaser should be all different results produced using spec2Fab, texture, subsurface scattering, caustics etc...}

@@

Computing material assignments at output device resolution is computationally inefficient. Because of this, material assignments are computed  using a reduced representation. We specify this representation using a Reducer Network.  This structure is conceptually similar to those used in programmable shading systems (e.g. ~\cite{Cook1984}, Maya Shader Networks) . However these systems are primarily concerned with assigning known materials and textures to an object's surface whereas we are seeking a volumetric assignment of (as yet) unknown materials. In order to accomplish this task we build a directed, acyclic graph which has the object's surface geometry as its root node. We define two classes of nodes, geometry nodes and parameterization nodes. A geometry node takes a volumetric region as input and produces a partition of unity of this region as output. The leaf nodes of our graph are the parameterization nodes which associate a material assignment function of the form $\lambda\left(x,y,z, \boldsymbol{\theta}\right)$ to an input volumetric region. 
$\lambda$ can either output material parameters or a discrete material assignment for a spatial point $\left(x,y,z\right)$ given some parameters, here denoted by $ \boldsymbol{\theta}$. We allow our material assignment nodes to assign a void material to regions of the mesh. This allows us to treat surface displacements and material assignments in a unified fashion. Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node. We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph, however, for material assignment problems this is neither required nor desired.

@@

\subsection{Tuners}
We define tuners as an abstract interface between a Reducer Node and an optimization algorithm.  Specifically a tuner is comprised of an optimization scheme, an error metric and a goal. Each tuner is attached to a specific geometric node in the Reducer Network. It then acts to optimize, or tune, the free variables associated with the subtree rooted at this node. One can think of this as a self-tuning shader network.  This organizational structure allows us to easily optimize subdomains of our object using different tuners. We provide a mechanism for scheduling tuner execution thus allowing both serial and parallel processing. 
\subsection{Tuning the Reducer Network}
\autoref{fig:tuner0} shows a typical workflow for a tuner.
\begin{figure}
\includegraphics[width=0.4\textwidth]{figure/tuner0.png}
\caption{Typical workflow for a Tuner.}
\label{fig:tuner0}
\end{figure}
A Tuner initializes its optimization procedure by querying the search space from its Reducer Node.
The Reducer Node computes the search space by traversing its sub-tree and collecting
free variables. The search space specifies the number of free variables, the type of each free variable
(discrete or continuous) and the bounds of these variables. 
With the search space specified, the Tuner's optimization subroutine executes.
The optimization subroutine may ask for additional information such as
the error value of a variable assignment and the gradient. These queries are answered
with call-back functions set up by the Tuner before executing the optimization subroutine. 
The call-back function typically performs the following three steps:
using Reducer Node to convert a variable assignment back to material assignment
function $\lambda$, running simulation with the new material assignment
and computing errors given the simulated result.
We note that our material function $\lambda$ can 
be efficiently evaluated by traversing the Reducer Network.
%I need to think about this
%We note that gradient computation of our material function $\lambda$ can also 
%be performed by efficiently traversing the Reducer Network.
\subsection{Tuner Network}
For many fabrication problems, tuners cannot act in isolation. For instance,  occasionally the best material at a given point in space is dependent upon the material assignment at nearby locations.  Tuning the free variables as if they were independent usually yields unsatisfactory results. Therefore, we allow the tuners to share information according to a user-specified graph structure.  This allows our framework to be interfaced with a wide range of existing graph based optimization and inference algorithms. For example, consider the Floyd–Steinberg dithering algorithm where the error of a pixel is distributed
to $4$ of its neighbors (right, lower left, down and lower right).  The graph structure of this algorithm is illustrated in Figure~\ref{fig:tuner}. The tuner is combined with the Reducer Network in Figure~\ref{fig:red1}. A simplified view of the combined graph is shown in Figure~\ref{fig:combine}. Executing each tuner in order is equivalent to running the Floyd–Steinberg dithering algorithm.
